{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-08 Paper_ttbarH_Draft.tex
KK edit to paragraph at the end of Sec. IIIB

In Sec.~\ref{sec3.1} we defined a fourth triple product,
$\epsilon_4 = \epsilon_3-\epsilon_2$.  We have constructed
an angular distribution related to this TP as well.
Specifically, we have analyzed the
$\Delta\phi(n_t,n_{\tbar})$ distribution in the $Q$ rest frame,
taking
$H$ to define the $z$-axis.  By studying the distributions
for various values of $\kp$ and $\kpt$, we have
found that they are not well described by Eq.~(\ref{eq27})
and their range of variation is larger than that of the distributions
displayed in Figs.~\ref{fig5} and \ref{fig6}.
{\bf (KK: I'm not sure what this means.  Are they less cosine-like?
  Or are the amplitudes or phase shifts larger than those for the other
  TPs?)}
Unlike the distributions
related to $\epsilon_1$-$\epsilon_3$, those arising from $\epsilon_4$
exhibit small changes in their shapes {\bf (KK: I don't think I understand
  this, since we said that the range of variation was larger in the last
  sentence.  I think I'm missing something :) )} for all the considered
hypotheses and for this reason we have not included the corresponding
plots here. However, the larger range of variation of the $\epsilon_4$
distributions leads to higher values for the asymmetry (as can be seen
from Tables \ref{table1} and \ref{table2}) even when the changes in
the respective shapes are smaller {\bf (KK: I don't understand what
  this means.)} than in the case of the
distributions described by Eq.~(\ref{eq27}).  \par
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mean value}
\label{sec3.3}
We turn now to consider the last type of observable that we will
construct from the TPs, the mean value. As was the case for the
observables considered in Secs.~\ref{sec3.1} and \ref{sec3.2},
the mean value is sensitive to $\kpt$.  Given a certain
TP, we define its mean value in the following manner,
%
\beq
\label{eq28}
\langle \epsilon \rangle = \frac{\int\epsilon\, [d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi]\,d\Phi}{\int [d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi]\,d\Phi},
\eeq
%
where $\Phi$ is the Lorentz-invariant phase space corresponding to the
final state
$b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H$. From
Eq.~(\ref{eq20}) we see that only the terms linear in (both) $\kp$ and $\kpt$
will contribute to the mean value.  Thus, we expect this observable
to be sensitive not only to the magnitude of $\kp\kpt$,
but also to the relative sign of
the couplings.\par

>>>>

In Sec.~\ref{sec3.1} we defined a fourth triple product,
$\epsilon_4 = \epsilon_3-\epsilon_2$.  We have constructed
an angular distribution related to this TP as well.
Specifically, we have analyzed the
$\Delta\phi(n_t,n_{\tbar})$ distribution in the $Q$ rest frame,
taking
$H$ to define the $z$-axis.  We have studied the distributions
for various values of $\kp$ and $\kpt$ and have
found that they are not well described by Eq.~(\ref{eq27}).
Instead of resembling sinusoids that are shifted to the left or
right for different values of the parameters, the distributions
remain peaked near $\Delta\phi(n_t,n_{\tbar})=0$, but become
slightly distorted in such a way that there is a non-zero
asymmetry [see Eq.~(\ref{eq26})].  Interestingly, while there
is not much visible change in the $\epsilon_4$ angular distribution
for different
parameter values, the associated asymmetry values are
larger than the asymmetries for the other TPs [see
  Tables \ref{table1} and \ref{table2}].  Since this angular
distribution does not exhibit much visible change for
different values of $\kp$ and $\kpt$, we do not include the corresponding
plots here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mean value}
\label{sec3.3}
We turn now to consider the last type of observable that we will
construct from the TPs, the mean value. As was the case for the
observables considered in Secs.~\ref{sec3.1} and \ref{sec3.2},
the mean value is sensitive to $\kpt$.  Given a certain
TP, we define its mean value in the following manner,
%
\beq
\label{eq28}
\langle \epsilon \rangle = \frac{\int\epsilon\, [d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi]\,d\Phi}{\int [d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi]\,d\Phi},
\eeq
%
where $\Phi$ is the Lorentz-invariant phase space corresponding to the
final state
$b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H$. From
Eq.~(\ref{eq20}) we see that only the terms linear in (both) $\kp$ and $\kpt$
will contribute to the mean value.  Thus, we expect this observable
to be sensitive not only to the magnitude of $\kp\kpt$,
but also to the relative sign of
the couplings.\par
